It still seems that black has hope in these extremely unfair variants of chess

### 2014-03-16 chesstego/paper.tex
Chessy crush v2 (v1 looks nearly fair). Mainline support

>>>>

\section{Chessy Crush Saga}

% \begin{itemize} % white
% \end{itemize} % white

\begin{figure}[ht]
\begin{center}
\chessboard[setfen=4k3/1ppppppp/8/8/8/1p1PP3/P1P2PPP/4K3]
\end{center}\vspace{-0.1in}
\caption{
  Black interfering with White's Omega Weapon main line:
  b3, d3, e3, c3 {\em (making candy)}, Rc2, Re2++. Black
  can progress pawns fast enough to capture White's. She
  can also move her King, making the candied rook less
  devastating. Ultimately, White's one-tempo advantage
  is not obviously winning.
}
\label{fig:chessyv1}
\end{figure}

\chessboard[setfen=4k3/ppp1pppp/8/8/3p4/2PP4/PP2PPPP/4K3]
